---
title: "hw-lego-trueman-wu"
output: html_notebook
---

```{r}
library(tidyverse)
library(dsbox)
```

```{r}
lego_sales
```

### Exercise 1.

In this sample, the first three common names of purchasers are Jackson, Jacob, and Joseph.

```{r}
lego_sales %>% 
  count(first_name) %>%
  arrange(desc(n)) %>%
  head(3)
```

### Exercise 2.

In this sample, the three most common themes of Lego sets purchased are Star Wars, Nexo Knights, and Gear.

```{r}
lego_sales %>% 
  count(theme) %>%
  arrange(desc(n)) %>%
  head(3)
```

### Exercise 3.

In this sample, the most common theme of Lego sets purchased is Star Wars. The most common sub-theme of Star Wars is The Force Awakens.

```{r}
most_common_theme <-lego_sales %>% 
  count(theme) %>%
  arrange(desc(n)) %>%
  head(1)[[1]]

lego_sales %>%
  filter(theme == most_common_theme) %>%
  count(subtheme) %>%
  arrange(desc(n)) %>%
  head(1)
```

### Exercise 4.

```{r}
lego_sales <- lego_sales %>%
  mutate(age_group = case_when(age <= 18 ~ "18 and under", age <= 25 & age >= 19 ~ "19 - 25", age <= 35 & age >= 26 ~ "26 - 35", age <= 50 & age >= 36 ~ "36 - 50", age >= 51 ~ "51 and over"))

lego_sales
```

### Exercise 5.

In this sample, the age group that purchase the highest number of Lego sets is 36 - 50.

```{r}
# each row may represent more than one set, depend on quantity

lego_sales %>% 
  group_by(age_group) %>%
  summarise(number_purchased = sum(quantity)) %>%
  arrange(desc(number_purchased))
```

### Exercise 6.

In this sample, the age group that spend the most money on Legos is 36 - 50.

```{r}
# us_price is price per set
# rows with same set_id with different quantity have the same us_price
# thus, money spend should be us_price * quantity

lego_sales %>% 
  group_by(age_group) %>%
  summarise(money_spent = sum(us_price * quantity)) %>%
  arrange(desc(money_spent))
```

### Exercise 7.

In this sample, the Lego theme that make the most money for Lego is Star Wars.

```{r}
lego_sales %>% 
  group_by(theme) %>%
  summarise(money_made = sum(us_price * quantity)) %>%
  arrange(desc(money_made))
```

### Exercise 8.

In this sample, most money are spent by people who don't leave their phone number; the known area code that spend the most money on Legos is 956.

```{r}
lego_sales %>% 
  mutate(area_code = str_sub(phone_number, 1, 3)) %>%
  group_by(area_code) %>%
  summarise(money_spent = sum(us_price * quantity)) %>%
  arrange(desc(money_spent))
```

### Exercise 9.

What is the most common sub theme within each theme?

Note that not all theme have a sub theme, not all lego set belong to a sub theme, and some themes have two equally common sub themes.

```{r}
theme_subtheme <- lego_sales %>% 
  count(theme, subtheme) %>%
  arrange(theme, desc(n))

theme_subtheme %>%
  group_by(theme) %>%
  summarise(n = max(n)) %>%
  merge(theme_subtheme) %>%
  select(theme, subtheme, n)
```

